{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-03 bmvc_review.tex
Revised the body a bit.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications on embedded systems. This is primarily because most of
embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy, at least, two criteria: minimal, manual intervention
after deployment and small footprint of consuming computational
resources and on executable code, with the assumption of reasonably
good performance. To this end, in this paper, we propose an ensemble
of the kernelized correlation filters (KCF), we call {\it E}nKCF, for
the problem of a single-target object tracking. In particular, we
developed a committee of KCFs to specifically address the scale-change
and dynamic maneuver of the target over frames. In addition, we
devised a Bayes filter for a smooth transition between individual
KCFs' executions. Experimental results showed that the performance of
ours are 70.10\% for precision on 20 pixels and 53.00\% for success
rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. In other
words, these results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123.
\end{abstract}

@@

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
is deployed on a low-end, embedded system.\footnote{We empirically
  found this computation reasonable -- the computation about an 1/10th
  scale down of computational resources from a typical PC to an
  embedded system.}

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, this
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
in an online fashion. In fact, a variant of the correlation filter,
the kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms, for example,
in VOT15 challenge, in terms of run-time and tracking
accuracy. However, a vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
primarily \cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target by just having multiple
correlation filters running on each frame could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
to the computational nature of correlation filter, however, this
approach would merely increase the computational complexity because it
has to run the correlation filter multiple times on each frame.

@@

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, they use the MOSSE tracker to estimate a target's
translation. And then they attemped to update the scale of the target
a way where the confidence map is used to determine the scale change
between successive frames. This is based on an assumption that the
scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation, but in a more efficient
way. To be more specific, we use an ensemble of KCFs in turn, instead
of running them all together on every frame. In particular, we deploy
three KCF in turn: \textit{target}+\textit{small background}
translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
($R_{s}$) and \textit{target}+\textit{large background} translation
filter ($R_{t}^{L}$). By doing so, we could still address the scale
change and estimate target's motion efficiently while increasing
run-time performance. Figure \ref{fig:Filters} shows examples of the
ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$. Figure
\ref{Workflows} illustrates the work-flow of the {\it E}nKCF.

\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
\end{tabular}
\caption{The workflow of {\it E}nKCF tracking algorithm.}
\label{Workflows}
\end{figure}

The contribution of this study is a novel, single-target tracking
algorithm running a very high-speed, $\geq 300$ fps. In particular,
the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCF, in
turn, to more effectively address the scale variance and the dynamic
maneuver of a target while preserving run-time performance as high as
possible. To minimize any potential performance gap from transiting
one KCF to another, we use a Bayes filter.

@@

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Figkure \ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
element-wise multiplication, resulting in a scale estimation in a
higher speed.

@@

After Henriques and his colleagues' presented impressive tracking 
results of KCF \cite{henriques2015high} on
VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
many variation of KCF were investigated. In particular,
\cite{ma2015long} and \cite{danelljan2014accurate} used a scale filter
to learn the target area only whereas \cite{li2014scale,
  bibi2015multi, tang2015multi} used a correlation filter learned on
the target area and its surrounding background in different size to
learn the optimal scale of the target. Our approach is particularly
similar to that of \cite{ma2015long} in that more than one KCF is used
to address the challenges of single target tracking. But ours is
different from that of \cite{ma2015long} in that we do not use those
multiple KCFs together at every frame, but alternatively at every
three frame. The way our algorithm is alternating multiple KCFs in
different goals intuitively makes sense in that the appearance of
consecutive images does not change drastically. Although it varies
based on the scene, learning a correlation filter a frame would not be
much different from the one learned using the image few or $k$ frames
later. By alternating three KCFs in turn, our algorithm runs as fast
as or faster than the original KCF. 
\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{This figure shows that there is marginal difference among the
  scale filters learned either at every frame or at every 5
  frames. The sub-figures at the top row show the scale filters
  trained from every frame and those at the bottom row show the scale
  filters estimated every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure}

The order of running these three KCFs is important as each of these
filters aims at addressing different challenges while preserving
run-time performance as fast as possible. The \textit{target+large
  background} translation filter, $R_{t}^{L}$, is intended to run
right after the scale filter, $R_s$, runs which is applied at every
$k=5$ frames. We run these two filters this way because we want to
minimize any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other frames
before $R_{S}$ and right after two consecutive frames running
$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$, uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the work-flow of the proposed algorithm
and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. We do not
have a separate pseudo-code for {\it E}nKCF2 as there are only two
differences between {\it E}nKCF and {\it E}nKCF2. First, the {\it
  E}nKCF2 runs $R_{t}^{L}$ every frame to better tackle large
ego-motion at low video frame rates. Second, we remove the particle
filter in the {\it E}nKCF2 tracker due to large ego-motion. In the
following section, we will briefly mention the theory behind the KCF.
\begin{algorithm}[h]
\small
	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{s}$ (Condition 1);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications deployed on embedded systems. This is primarily because
most of embedded systems already have image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy, at least, two criteria: minimal, manual intervention
after deployment and small footprint of consuming computational
resources and on executable code, with the assumption of reasonably
good performance. To this end, in this paper, we propose an ensemble
of the kernelized correlation filters (KCF), we call {\it E}nKCF, for
the problem of a single-target object tracking. In particular, we
developed a committee of KCFs to specifically address the scale-change
and dynamic maneuver of the target over frames. In addition, we
developed a Bayes filter for a smooth transition between individual
KCFs' executions. Experimental results showed that the performance of
ours are 70.10\% for precision at 20 pixels and 53.00\% for success
rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
results showed that our method is better than existing ones over 5\%
on precision on 20 pixels and 10-20\% on AUC on average. Moreover our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps) for UAV123.
\end{abstract}

@@

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. Specifically, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
is deployed on a low-end, embedded system.\footnote{We empirically
  found this computation reasonable -- the computation about an 1/10th
  scale down of computational resources from a typical PC to an
  embedded system.}

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, this
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
in an online fashion. In fact, a variant of the correlation filter,
the kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms, for example,
in VOT15 challenge, in terms of run-time and tracking
accuracy. However, a vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
primarily \cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target by just having multiple
correlation filters running on each frame could reduce the run-time
performance from 300 to 100 fps. An intuitive way of addressing the
scale change is to scan the region of interest (ROI) with templates in
different dimensions based on pre-defined scale ratios to find the
target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
to the computational nature of correlation filter, however, this
approach would merely increase the computational complexity because it
has to run the correlation filter multiple times on each frame.

@@

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, they use the MOSSE tracker to estimate a target's
translation. And then they attemped to update the scale of the target
a way where the confidence map is used to determine the scale change
between successive frames. This is based on an assumption that the
scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation, but in a more efficient
way. To be more specific, we use an ensemble of KCFs in turn, instead
of running them all together on every frame. In particular, we deploy
three KCF in turn: \textit{target}+\textit{small background}
translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
($R_{s}$) and \textit{target}+\textit{large background} translation
filter ($R_{t}^{L}$). By doing so, we could still address the scale
change and estimate target's motion efficiently while increasing
run-time performance. Figure \ref{fig:Filters} shows examples of the
region of interest (ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and
$R_{s}$. Figure \ref{Workflows} illustrates the work-flow of the {\it
  E}nKCF.
\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
\end{tabular}
\caption{The workflow of {\it E}nKCF tracking algorithm.}
\label{Workflows}
\end{figure}
The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps. In particular,
the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCF, in
turn, to more effectively address the scale variance and the dynamic
maneuver of a target while preserving run-time performance as high as
possible. To minimize any potential performance gap from transiting
one KCF to another, we use a Bayes filter.

@@

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Figkure \ref{fig:Filters} shows examples
of the ROI covered by each of three filters. We believe that a filter
for learning a target's translation should include its background. In
addition, making the ROI for the scale filter, $R_{s}$, tighter
reduces the size of the template for the element-wise multiplication,
resulting in a scale estimation in a higher speed.

@@

After Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. In particular, \cite{ma2015long}
and \cite{danelljan2014accurate} used a scale filter to learn the
target area only whereas \cite{li2014scale, bibi2015multi,
  tang2015multi} used a correlation filter learned on the target area
and its surrounding background in different size to learn the optimal
scale of the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those multiple KCFs
together at every frame, but alternatively at every three frame. The
way our algorithm is alternating multiple KCFs in different goals
intuitively makes sense in that the appearance of consecutive images
does not change drastically. Although it varies based on the scene,
learning a correlation filter a frame would not be much different from
the one learned using the image few or $k$ frames later. Figure
\ref{fig:Filters_Comparison} shows examples supporting this
observation.
\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{This figure shows that there is marginal difference among the
  scale filters learned either at every frame or at every 5
  frames. The sub-figures at the top row show the scale filters
  trained from every frame and those at the bottom row show the scale
  filters estimated every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure}

{\it Burak: What we wrote here didn't match what you told me. Go over
  the following paragraph and change the numbers correctly.}

The order of running these three KCFs is important because each of
these filters aims at addressing different challenges; The
\textit{target+large background} translation filter, $R_{t}^{L}$, is
applied to the $i$th image frame, another translation filter,
$R_{t}^{S}$ is applied to the $i+1$th image frame, and then the scale
filter, $R_{s}$ is applied to the $i+2$the image. This order repeats
until the end of the image frames. The translation filter,
$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
runs which is applied at every other $i+2$ frames. We run these two
filters this way because we want to minimize any drifts that are
likely to happen running only $R_{s}$. In addition, the filter,
$R_{t}^{S}$, is applied to every other frames before $R_{s}$ and right
after two consecutive frames running $R_{t}^{L}$. By iterating this
order of learning KCFs, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$, uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflows} illustrates the work-flow of the proposed algorithm
and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.

{\it Burak: Remove this EnKCF2 part from the text and from the pseudo code.}

We do not have a separate pseudo-code for {\it E}nKCF2 as there are
only two differences between {\it E}nKCF and {\it E}nKCF2. First, the
{\it E}nKCF2 runs $R_{t}^{L}$ every frame to better tackle large
ego-motion at low video frame rates. Second, we remove the particle
filter in the {\it E}nKCF2 tracker due to large ego-motion. In the
following section, we will briefly mention the theory behind the KCF.
\begin{algorithm}[h]
\small
	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
			    \State Update $R_{s}$ (Condition 1);
			    \State Update $R_{t}^{L}$ (Condition 2);
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}
